---
title: "Joining LC Codes to E-Usage"
author: "Alexander Harriman"
date: "2026-05-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



This file finds the LC codes for as many titles with e-usage as possible. 


```{r, warning = FALSE}
reticulate::py_config()
library(readxl)
library(RSQLite)
library(DBI)
library(dplyr)
library(tidyverse)
library(stringr)
library(writexl)
library(fuzzywuzzyR)
```



# Load the Alma Data


The data in these two Excel files can be found in the Alma Analytics files of the same name. They are split into two files, since an Excel file is not large enough to fit all rows.

```{r, warning = FALSE}
setwd('C:\\Users\\aharrima\\OneDrive - University of Tennessee\\Documents\\One-Off Usage Analysis\\Adding LC Codes to Usage') #Set this to the data's location on your local computer!

almaData1 <- read_excel('Alma Electronic Collection ISSNs and ISBNs for Usage Joining Part 1 Aug 2026.xlsx') 

almaData2 <- read_excel('Alma Electronic Collection ISSNs and ISBNs for Usage Joining Part 2 Aug 2026.xlsx')

almaData <- rbind(almaData1, almaData2) |>
  distinct()
```




# Use Subjects to Find LC for Unknown Items


Alma's subject information on each item may be able to help us identify its LC code when the LC code is Unknown.


## Get the Unknown Titles

```{r}
almaUnknown <- almaData |>
  filter(`Classification Code` == 'Unknown')

almaUnknown
```


## Assign LC Codes by Subject

As new subjects appear or as new information on how to assign certain subjects is figured out, add or edit grepl() statements in the block below. LC codes are assigned in the order they appear below, so make sure all confident assignments are close to the top.


```{r}
assignedLCUnknown <- almaUnknown |>
  mutate(`Classification Code` = case_when(
    # Clear Identifiers
    grepl('Engineering', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Comput', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Information technology', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Three-dimensional imaging', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Math', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Algebra', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Circuits', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Economic', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Medic', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Endocrine', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Wireless', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Satellites', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Navy', Subjects, ignore.case = TRUE) == TRUE ~ 'V',
    grepl('Air Force', Subjects, ignore.case = TRUE) == TRUE ~ 'U',
    grepl('Army', Subjects, ignore.case = TRUE) == TRUE ~ 'U',
    grepl('Internet', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Robot', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Artificial intelligence', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',  
    grepl('Accounting', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Bank', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Social sciences', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Commerce', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Health', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Philosophy', Subjects, ignore.case = TRUE) == TRUE ~ 'B',
    grepl('languages', Subjects, ignore.case = TRUE) == TRUE ~ 'P',
    grepl('Surgery', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Agricultur', Subjects, ignore.case = TRUE) == TRUE ~ 'S',
    grepl('Kidney', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Nurs', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Military', Subjects, ignore.case = TRUE) == TRUE ~ 'U',
    grepl('Hedge fund', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('econòmique', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Ortho', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Business', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Treatment', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Homosexual', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Patient', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Fruit', Subjects, ignore.case = TRUE) == TRUE ~ 'S',
    grepl('Automobile', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Baseball', Subjects, ignore.case = TRUE) == TRUE ~ 'G',
    grepl('Wrestling', Subjects, ignore.case = TRUE) == TRUE ~ 'G',
    grepl('Software', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Aeronautics', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Airplane', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Airport', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Chemistry', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Horticultur', Subjects, ignore.case = TRUE) == TRUE ~ 'S',
    grepl('Advertis', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Anesthe', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Archbishop', Subjects, ignore.case = TRUE) == TRUE ~ 'B',
    grepl('Linguistics', Subjects, ignore.case = TRUE) == TRUE ~ 'P',
    grepl('Architect', Subjects, ignore.case = TRUE) == TRUE ~ 'N',
    grepl('Education', Subjects, ignore.case = TRUE) == TRUE ~ 'L',
    grepl('Tinnitus', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Cancer', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Astro', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Atom', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Automat', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Bible', Subjects, ignore.case = TRUE) == TRUE ~ 'B',
    grepl('Bibliography', Subjects, ignore.case = TRUE) == TRUE ~ 'Z',
    grepl('Almanac', Subjects, ignore.case = TRUE) == TRUE ~ 'A',
    grepl('Botany', Subjects, ignore.case = TRUE) == TRUE ~ 'S',
    grepl('Building', Subjects, ignore.case = TRUE) == TRUE ~ 'N',
    grepl('Church', Subjects, ignore.case = TRUE) == TRUE ~ 'B',
    grepl('Music', Subjects, ignore.case = TRUE) == TRUE ~ 'N',
    grepl('Cloning', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Christian', Subjects, ignore.case = TRUE) == TRUE ~ 'B',
    grepl('Buddhi', Subjects, ignore.case = TRUE) == TRUE ~ 'B',
    grepl('Economy', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Finance', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Physics', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Court', Subjects, ignore.case = TRUE) == TRUE ~ 'K',
    grepl('Criminal', Subjects, ignore.case = TRUE) == TRUE ~ 'K',
    grepl('Data', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Dentist', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Equation', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Credit', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Econometrics', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Funds', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Electric', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Poetry', Subjects, ignore.case = TRUE) == TRUE ~ 'P',
    grepl('Psych', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Religion', Subjects, ignore.case = TRUE) == TRUE ~ 'B',
    grepl('Arachnida', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Archery', Subjects, ignore.case = TRUE) == TRUE ~ 'G',
    grepl('Language', Subjects, ignore.case = TRUE) == TRUE ~ 'P',
    grepl('Bacteri', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Variable', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Breeding', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Capitalism', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Climat', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Pollution', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Brain', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Bone', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Chiropractic', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Geometry', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Diabetes', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Libraries', Subjects, ignore.case = TRUE) == TRUE ~ 'Z',
    grepl('Dynamics', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Migration', Subjects, ignore.case = TRUE) == TRUE ~ 'J',
    grepl('Drama', Subjects, ignore.case = TRUE) == TRUE ~ 'N',
    grepl('Justice', Subjects, ignore.case = TRUE) == TRUE ~ 'K',
    grepl('Fluid', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Football', Subjects, ignore.case = TRUE) == TRUE ~ 'G',
    grepl('Genom', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Geograph', Subjects, ignore.case = TRUE) == TRUE ~ 'G',
    grepl('Britain', Subjects, ignore.case = TRUE) == TRUE ~ 'D',
    grepl('Latin America', Subjects, ignore.case = TRUE) == TRUE ~ 'F',
    grepl('Agronomy', Subjects, ignore.case = TRUE) == TRUE ~ 'S',
    grepl('Craniofacial', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Dairy', Subjects, ignore.case = TRUE) == TRUE ~ 'S',
    grepl('Detector', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Diagnostic imaging', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Marriage', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Drone', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Election', Subjects, ignore.case = TRUE) == TRUE ~ 'J',
    grepl('Ethics', Subjects, ignore.case = TRUE) == TRUE ~ 'B',
    grepl('Feeds', Subjects, ignore.case = TRUE) == TRUE ~ 'S',
    grepl('Hunting', Subjects, ignore.case = TRUE) == TRUE ~ 'G',
    grepl('Plant', Subjects, ignore.case = TRUE) == TRUE ~ 'S',
    grepl('Freemason', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Gay', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Social & cultural', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Hospital', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Genetics', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Image processing', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('International relation', Subjects, ignore.case = TRUE) == TRUE ~ 'J',
    grepl('Film', Subjects, ignore.case = TRUE) == TRUE ~ 'N',
    grepl('Judaism', Subjects, ignore.case = TRUE) == TRUE ~ 'B',
    grepl('Jesus', Subjects, ignore.case = TRUE) == TRUE ~ 'B',
    grepl('Lasers', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Machine learning', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Manufactur', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Mechanics', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Motor', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Multibody', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Naturopathy', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Optometry', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Paint', Subjects, ignore.case = TRUE) == TRUE ~ 'N',
    grepl('Pediatric', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Phenotype', Subjects, ignore.case = TRUE) == TRUE ~ 'S',
    grepl('Physical therapy', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Probabilit', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Quantum', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Camping', Subjects, ignore.case = TRUE) == TRUE ~ 'G',
    grepl('Sex', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Sound', Subjects, ignore.case = TRUE) == TRUE ~ 'M',
    grepl('Statistic', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Teach', Subjects, ignore.case = TRUE) == TRUE ~ 'L',
    grepl('Tech', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    

    


    
    # Generalities
    grepl('Newspaper', Subjects, ignore.case = TRUE) == TRUE ~ 'P',
    grepl('Literature', Subjects, ignore.case = TRUE) == TRUE ~ 'P',
    grepl('Electronic', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Energy', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('IEEE', Title, ignore.case = FALSE) == TRUE ~ 'T',
    grepl('Art', Subjects, ignore.case = TRUE) == TRUE ~ 'N',
    grepl('Signal', Subjects, ignore.case = TRUE) == TRUE ~ 'T', 
    grepl('ology', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Electro', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Transportation', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Care', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Sport', Subjects, ignore.case = TRUE) == TRUE ~ 'G',   
    grepl('trade', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Bio', Subjects, ignore.case = TRUE) == TRUE ~ 'R',   
    grepl('Pharma', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('fitness', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Tele', Subjects, ignore.case = TRUE) == TRUE ~ 'T',
    grepl('Big data', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Canad', Subjects, ignore.case = TRUE) == TRUE ~ 'F',
    grepl('Australia', Subjects, ignore.case = TRUE) == TRUE ~ 'D',
    grepl('Africa', Subjects, ignore.case = TRUE) == TRUE ~ 'D',
    grepl('Alberta', Subjects, ignore.case = TRUE) == TRUE ~ 'F',
    grepl('Disease', Subjects, ignore.case = TRUE) == TRUE ~ 'R',
    grepl('Asia', Subjects, ignore.case = TRUE) == TRUE ~ 'D',
    grepl('China', Subjects, ignore.case = TRUE) == TRUE ~ 'D',
    grepl('Science', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Government', Subjects, ignore.case = TRUE) == TRUE ~ 'J',
    grepl('Baker', Subjects, ignore.case = TRUE) == TRUE ~ 'N',
    grepl('Cooking', Subjects, ignore.case = TRUE) == TRUE ~ 'N',
    grepl('Law', Subjects, ignore.case = TRUE) == TRUE ~ 'K',
    grepl('Industry', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Brasil', Subjects, ignore.case = TRUE) == TRUE ~ 'F',
    grepl('British Columbia', Subjects, ignore.case = TRUE) == TRUE ~ 'F',
    grepl('Communication', Subjects, ignore.case = TRUE) == TRUE ~ 'P',    
    grepl('Color', Subjects, ignore.case = TRUE) == TRUE ~ 'N',
    grepl('Matter', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Employee', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Environment', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Europe', Subjects, ignore.case = TRUE) == TRUE ~ 'D',
    grepl('Analysis', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Graph', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Politics', Subjects, ignore.case = TRUE) == TRUE ~ 'J',
    grepl('Compounds', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Market', Subjects, ignore.case = TRUE) == TRUE ~ 'H',
    grepl('Theory', Subjects, ignore.case = TRUE) == TRUE ~ 'Q',
    grepl('Plant', Subjects, ignore.case = TRUE) == TRUE ~ 'S',
    grepl('Social ', Subjects, ignore.case = TRUE) == TRUE ~ 'H',    
    
    .default = 'Unknown'
  ))

assignedLCUnknown
```




## Replace the Unknown LCs with the Assumed LCs


```{r}
knownLC <- almaData |>
  filter(`Classification Code` != 'Unknown')

almaDataFixedLC <- rbind(knownLC, assignedLCUnknown)
```




## Split Cells with Multiple ISSNs or ISBNs


This is so the ISSN/ISBNs can be joined together.

```{r}
almaDataISSN <- almaDataFixedLC |>
  filter(is.na(ISSN) == FALSE) |>
  mutate(ISSN = str_replace_all(ISSN, "-", "")) |>
  select(Title, `Classification Code`, ISSN) |>
  distinct()

almaDataISBN <- almaDataFixedLC |>
  filter(is.na(ISBN) == FALSE) |>
  mutate(ISBN = str_replace_all(ISBN, "-", "")) |>
  select(Title, `Classification Code`, ISBN) |>
  distinct()

almaDataISSN2 <- almaDataISSN |>
  select(Title, `Classification Code`, ISSN) 

almaDataISSN2 <- separate_rows(almaDataISSN2, ISSN, sep = ';')

almaDataISSN2 <- almaDataISSN2 |>
  mutate(ISSN = str_trim(ISSN))

almaDataISBN2 <- almaDataISBN |>
  select(Title, `Classification Code`, ISBN)

almaDataISBN2 <- separate_rows(almaDataISBN2, ISBN, sep = ';')

almaDataISBN2 <- almaDataISBN2 |>
  mutate(ISBN = str_trim(ISBN))
```



# Load the Title Report

This will use the TR_Archive report from the Big Usage Database.

```{r}
con <- dbConnect(SQLite(), "C:\\Users\\aharrima\\OneDrive - University of Tennessee\\Documents\\Big_Usage_Database_Updated.db")

TR_ID <- dbGetQuery(con,
                    "SELECT *
                    FROM TR_Archive
                    WHERE Metric_Type == 'Unique_Item_Requests'
                    AND (Online_ISSN != 'Unknown' OR Print_ISSN != 'Unknown' OR ISBN != 'Unknown')
                    ORDER BY Title")


dim(TR_ID)
```

# Clean Down to FY Usage Only

FOR EACH NEW SEMESTER, add new months (and a new FY column if needed) to ensure accurate data.

```{r}
TR_ID <- TR_ID |>
  mutate(FY21 = ifelse(is.na(`Jan-2021`) == TRUE, 0, `Jan-2021`)
              + ifelse(is.na(`Feb-2021`) == TRUE, 0, `Feb-2021`)
              + ifelse(is.na(`Mar-2021`) == TRUE, 0, `Mar-2021`)
              + ifelse(is.na(`Apr-2021`) == TRUE, 0, `Apr-2021`)
              + ifelse(is.na(`May-2021`) == TRUE, 0, `May-2021`)
              + ifelse(is.na(`Jun-2021`) == TRUE, 0, `Jun-2021`),
         FY22 = ifelse(is.na(`Jul-2021`) == TRUE, 0, `Jul-2021`)
              + ifelse(is.na(`Aug-2021`) == TRUE, 0, `Aug-2021`)
              + ifelse(is.na(`Sep-2021`) == TRUE, 0, `Sep-2021`)
              + ifelse(is.na(`Oct-2021`) == TRUE, 0, `Oct-2021`)
              + ifelse(is.na(`Nov-2021`) == TRUE, 0, `Nov-2021`)
              + ifelse(is.na(`Dec-2021`) == TRUE, 0, `Dec-2021`)
              + ifelse(is.na(`Jan-2022`) == TRUE, 0, `Jan-2022`)
              + ifelse(is.na(`Feb-2022`) == TRUE, 0, `Feb-2022`)
              + ifelse(is.na(`Mar-2022`) == TRUE, 0, `Mar-2022`)
              + ifelse(is.na(`Apr-2022`) == TRUE, 0, `Apr-2022`)
              + ifelse(is.na(`May-2022`) == TRUE, 0, `May-2022`)
              + ifelse(is.na(`Jun-2022`) == TRUE, 0, `Jun-2022`),
         FY23 = ifelse(is.na(`Jul-2022`) == TRUE, 0, `Jul-2022`)
              + ifelse(is.na(`Aug-2022`) == TRUE, 0, `Aug-2022`)
              + ifelse(is.na(`Sep-2022`) == TRUE, 0, `Sep-2022`)
              + ifelse(is.na(`Oct-2022`) == TRUE, 0, `Oct-2022`)
              + ifelse(is.na(`Nov-2022`) == TRUE, 0, `Nov-2022`)
              + ifelse(is.na(`Dec-2022`) == TRUE, 0, `Dec-2022`)
              + ifelse(is.na(`Jan-2023`) == TRUE, 0, `Jan-2023`)
              + ifelse(is.na(`Feb-2023`) == TRUE, 0, `Feb-2023`)
              + ifelse(is.na(`Mar-2023`) == TRUE, 0, `Mar-2023`)
              + ifelse(is.na(`Apr-2023`) == TRUE, 0, `Apr-2023`)
              + ifelse(is.na(`May-2023`) == TRUE, 0, `May-2023`)
              + ifelse(is.na(`Jun-2023`) == TRUE, 0, `Jun-2023`),
         FY24 = ifelse(is.na(`Jul-2023`) == TRUE, 0, `Jul-2023`)
              + ifelse(is.na(`Aug-2023`) == TRUE, 0, `Aug-2023`)
              + ifelse(is.na(`Sep-2023`) == TRUE, 0, `Sep-2023`)
              + ifelse(is.na(`Oct-2023`) == TRUE, 0, `Oct-2023`)
              + ifelse(is.na(`Nov-2023`) == TRUE, 0, `Nov-2023`)
              + ifelse(is.na(`Dec-2023`) == TRUE, 0, `Dec-2023`)
              + ifelse(is.na(`Jan-2024`) == TRUE, 0, `Jan-2024`)
              + ifelse(is.na(`Feb-2024`) == TRUE, 0, `Feb-2024`)
              + ifelse(is.na(`Mar-2024`) == TRUE, 0, `Mar-2024`)
              + ifelse(is.na(`Apr-2024`) == TRUE, 0, `Apr-2024`)
              + ifelse(is.na(`May-2024`) == TRUE, 0, `May-2024`)
              + ifelse(is.na(`Jun-2024`) == TRUE, 0, `Jun-2024`),
         FY25 = ifelse(is.na(`Jul-2024`) == TRUE, 0, `Jul-2024`)
              + ifelse(is.na(`Aug-2024`) == TRUE, 0, `Aug-2024`)
              + ifelse(is.na(`Sep-2024`) == TRUE, 0, `Sep-2024`)
              + ifelse(is.na(`Oct-2024`) == TRUE, 0, `Oct-2024`)
              + ifelse(is.na(`Nov-2024`) == TRUE, 0, `Nov-2024`)
              + ifelse(is.na(`Dec-2024`) == TRUE, 0, `Dec-2024`)
              + ifelse(is.na(`Jan-2025`) == TRUE, 0, `Jan-2025`)
              + ifelse(is.na(`Feb-2025`) == TRUE, 0, `Feb-2025`)
              + ifelse(is.na(`Mar-2025`) == TRUE, 0, `Mar-2025`)
              + ifelse(is.na(`Apr-2025`) == TRUE, 0, `Apr-2025`)
              + ifelse(is.na(`May-2025`) == TRUE, 0, `May-2025`)
              + ifelse(is.na(`Jun-2025`) == TRUE, 0, `Jun-2025`),
         FY26 = ifelse(is.na(`Jul-2025`) == TRUE, 0, `Jul-2025`)
              + ifelse(is.na(`Aug-2025`) == TRUE, 0, `Aug-2025`)
              + ifelse(is.na(`Sep-2025`) == TRUE, 0, `Sep-2025`)
              + ifelse(is.na(`Oct-2025`) == TRUE, 0, `Oct-2025`)
              + ifelse(is.na(`Nov-2025`) == TRUE, 0, `Nov-2025`)
              + ifelse(is.na(`Dec-2025`) == TRUE, 0, `Dec-2025`)
              + ifelse(is.na(`Jan-2026`) == TRUE, 0, `Jan-2026`)
              + ifelse(is.na(`Feb-2026`) == TRUE, 0, `Feb-2026`)
              + ifelse(is.na(`Mar-2026`) == TRUE, 0, `Mar-2026`)
              + ifelse(is.na(`Apr-2026`) == TRUE, 0, `Apr-2026`)
              + ifelse(is.na(`May-2026`) == TRUE, 0, `May-2026`)
              + ifelse(is.na(`Jun-2026`) == TRUE, 0, `Jun-2026`)) |>
  select(Title, Online_ISSN, Print_ISSN, ISBN, Vendor, FY21, FY22, FY23, FY24, FY25, FY26, Reporting_Period_Total, index)


```



# Join the Alma holdings to the Usage


```{r, warning = FALSE}
joinedE <- inner_join(TR_ID, almaDataISSN2, by = c('Online_ISSN' = 'ISSN')) |>
  distinct()

joinedP <- inner_join(TR_ID, almaDataISSN2, by = c('Print_ISSN' = 'ISSN')) |>
  distinct()

joinedISBN <- inner_join(TR_ID, almaDataISBN2, by = c('ISBN' = 'ISBN')) |>
  distinct()

joined <- rbind(joinedE, joinedP, joinedISBN) |>
  distinct() |>
  mutate(Row_ID = row_number())

joined
```



# Remove Duplicated Indexes in the Joined File

Some of the Alma holdings have ISBN or ISSN leakage, causing multiple titles and multiple LC codes to bleed into one usage line. Using fuzzy matching for the titles, the most likely match for these titles will be used to assign a single LC code for each title.


## Find Double Row Candidates


```{r}
joinedDoubleIndex <- joined |>
  group_by(index) |>
  summarise(n = n()) |>
  filter(n > 1)

joinedDoubleIndex
```


## Remove Wrong Lines

This may take many minutes (even upwards of multiple hours depending on length) to finish. R will continue to run even if the computer is in sleep mode, but you will not be able to run any other R code (and this may also take up significant RAM).

```{r}
 for(i in 1:length(unique(joinedDoubleIndex$index))){

   if(joinedDoubleIndex$index[i] == 72411){ #This is a known error that can be skipped - the exact number might change with each semester, so keep this in mind
     next
   }
   
   
   if(i %% 2500 == 0){
     print(i)
   }

   options <- joined |>
     filter(index == joinedDoubleIndex$index[i])

   titleName <- options$Title.x[1]

   matchTest <- GetCloseMatches(string = titleName, sequence_strings = options$Title.y, n = 1L, cutoff = 0.01)

   removeLines <- options |>
     filter(Title.y != matchTest)
   
   joined <- joined |>
     filter(!Row_ID %in% removeLines$Row_ID)
 }
```

Once this code block is run, stop! Run the joinedDoubleIndex block again. That way, there won't be any time lost to duplicated work in the next cleaning step.


```{r}
joinedDoubleIndex <- joined |>
  group_by(index) |>
  summarise(n = n()) |>
  filter(n > 1)

joinedDoubleIndex
```


## Remove the True Duplicates

For the titles with two exact copies, the last row's LC code will be chosen to stay consistent. This will be applied to all titles whose fuzzy match did not produce a clear winner (make sure the above cells have finished before running this).

This may also take several minutes to run, but should be much shorter than the first block.

```{r}
 for(i in 1:length(unique(joinedDoubleIndex$index))){

   if(i %% 1000 == 0){
     print(i)
   }

   options <- joined |>
     filter(index == joinedDoubleIndex$index[i])
   
   removeLines <- head(options, 1)
   
   joined <- joined |>
     filter(!Row_ID %in% removeLines$Row_ID)
 }
```


Before continuing, make sure that all doubled indexes have just one row remaining. If you run this block below and see more than 0 rows in joinedDoubleIndex, then run the above cell block again until there are 0 remaining.

```{r}
joinedDoubleIndex <- joined |>
  group_by(index) |>
  summarise(n = n()) |>
  filter(n > 1)

joinedDoubleIndex
```


## Export the Data

Make sure this is only run once the above cell returns a 0-row data table.

```{r, warning = FALSE}
setwd('C:\\Users\\aharrima\\OneDrive - University of Tennessee\\Documents\\One-Off Usage Analysis\\Adding LC Codes to Usage')

write_xlsx(joined, 'De-Duplicated Joined Titles With Fiscal Year Usage Aug 2026.xlsx')
```


## Find the Missing LC Titles


These titles have usage, but were not joined to an Alma holding. These will be treated as no-information titles in the Unknown section to attempt to catch their LC code.


```{r, warning = FALSE}
usageJoinMisses <- TR_ID |>
  filter(!index %in% joined$index) |>
  select(Title, Vendor, Online_ISSN, Print_ISSN, ISBN, FY21, FY22, FY23, FY24, FY25, FY26, Reporting_Period_Total) |>
  mutate(`Classification Code` = 'Not Available')

colnames(usageJoinMisses) <- c('Title', 'Vendor', 'Online_ISSN', 'Print_ISSN', 'ISBN', 'FY21', 'FY22', 'FY23', 'FY24', 'FY25', 'FY26', 'Reporting_Period_Total', 'Classification Code')

usageJoinMisses
```



# Find the Titles with No Identifiers


These titles have usage with no ISBN nor ISSN information. We can attempt to assume their LC code based on their vendor or key words within their titles.


```{r}
con <- dbConnect(SQLite(), "C:\\Users\\aharrima\\OneDrive - University of Tennessee\\Documents\\Big_Usage_Database_Updated.db")

TR_No_ID <- dbGetQuery(con,
                    "SELECT *
                    FROM TR_Archive
                    WHERE Metric_Type == 'Unique_Item_Requests'
                    AND Online_ISSN == 'Unknown' AND Print_ISSN == 'Unknown' AND ISBN == 'Unknown'
                    ORDER BY Title")


dim(TR_No_ID)
```



# Clean Down to FY Usage Only


FOR EACH NEW SEMESTER, do the same thing as the similar TR_ID block above.

```{r}
TR_No_ID <- TR_No_ID |>
  mutate(FY21 = ifelse(is.na(`Jan-2021`) == TRUE, 0, `Jan-2021`)
              + ifelse(is.na(`Feb-2021`) == TRUE, 0, `Feb-2021`)
              + ifelse(is.na(`Mar-2021`) == TRUE, 0, `Mar-2021`)
              + ifelse(is.na(`Apr-2021`) == TRUE, 0, `Apr-2021`)
              + ifelse(is.na(`May-2021`) == TRUE, 0, `May-2021`)
              + ifelse(is.na(`Jun-2021`) == TRUE, 0, `Jun-2021`),
         FY22 = ifelse(is.na(`Jul-2021`) == TRUE, 0, `Jul-2021`)
              + ifelse(is.na(`Aug-2021`) == TRUE, 0, `Aug-2021`)
              + ifelse(is.na(`Sep-2021`) == TRUE, 0, `Sep-2021`)
              + ifelse(is.na(`Oct-2021`) == TRUE, 0, `Oct-2021`)
              + ifelse(is.na(`Nov-2021`) == TRUE, 0, `Nov-2021`)
              + ifelse(is.na(`Dec-2021`) == TRUE, 0, `Dec-2021`)
              + ifelse(is.na(`Jan-2022`) == TRUE, 0, `Jan-2022`)
              + ifelse(is.na(`Feb-2022`) == TRUE, 0, `Feb-2022`)
              + ifelse(is.na(`Mar-2022`) == TRUE, 0, `Mar-2022`)
              + ifelse(is.na(`Apr-2022`) == TRUE, 0, `Apr-2022`)
              + ifelse(is.na(`May-2022`) == TRUE, 0, `May-2022`)
              + ifelse(is.na(`Jun-2022`) == TRUE, 0, `Jun-2022`),
         FY23 = ifelse(is.na(`Jul-2022`) == TRUE, 0, `Jul-2022`)
              + ifelse(is.na(`Aug-2022`) == TRUE, 0, `Aug-2022`)
              + ifelse(is.na(`Sep-2022`) == TRUE, 0, `Sep-2022`)
              + ifelse(is.na(`Oct-2022`) == TRUE, 0, `Oct-2022`)
              + ifelse(is.na(`Nov-2022`) == TRUE, 0, `Nov-2022`)
              + ifelse(is.na(`Dec-2022`) == TRUE, 0, `Dec-2022`)
              + ifelse(is.na(`Jan-2023`) == TRUE, 0, `Jan-2023`)
              + ifelse(is.na(`Feb-2023`) == TRUE, 0, `Feb-2023`)
              + ifelse(is.na(`Mar-2023`) == TRUE, 0, `Mar-2023`)
              + ifelse(is.na(`Apr-2023`) == TRUE, 0, `Apr-2023`)
              + ifelse(is.na(`May-2023`) == TRUE, 0, `May-2023`)
              + ifelse(is.na(`Jun-2023`) == TRUE, 0, `Jun-2023`),
         FY24 = ifelse(is.na(`Jul-2023`) == TRUE, 0, `Jul-2023`)
              + ifelse(is.na(`Aug-2023`) == TRUE, 0, `Aug-2023`)
              + ifelse(is.na(`Sep-2023`) == TRUE, 0, `Sep-2023`)
              + ifelse(is.na(`Oct-2023`) == TRUE, 0, `Oct-2023`)
              + ifelse(is.na(`Nov-2023`) == TRUE, 0, `Nov-2023`)
              + ifelse(is.na(`Dec-2023`) == TRUE, 0, `Dec-2023`)
              + ifelse(is.na(`Jan-2024`) == TRUE, 0, `Jan-2024`)
              + ifelse(is.na(`Feb-2024`) == TRUE, 0, `Feb-2024`)
              + ifelse(is.na(`Mar-2024`) == TRUE, 0, `Mar-2024`)
              + ifelse(is.na(`Apr-2024`) == TRUE, 0, `Apr-2024`)
              + ifelse(is.na(`May-2024`) == TRUE, 0, `May-2024`)
              + ifelse(is.na(`Jun-2024`) == TRUE, 0, `Jun-2024`),
         FY25 = ifelse(is.na(`Jul-2024`) == TRUE, 0, `Jul-2024`)
              + ifelse(is.na(`Aug-2024`) == TRUE, 0, `Aug-2024`)
              + ifelse(is.na(`Sep-2024`) == TRUE, 0, `Sep-2024`)
              + ifelse(is.na(`Oct-2024`) == TRUE, 0, `Oct-2024`)
              + ifelse(is.na(`Nov-2024`) == TRUE, 0, `Nov-2024`)
              + ifelse(is.na(`Dec-2024`) == TRUE, 0, `Dec-2024`)
              + ifelse(is.na(`Jan-2025`) == TRUE, 0, `Jan-2025`)
              + ifelse(is.na(`Feb-2025`) == TRUE, 0, `Feb-2025`)
              + ifelse(is.na(`Mar-2025`) == TRUE, 0, `Mar-2025`)
              + ifelse(is.na(`Apr-2025`) == TRUE, 0, `Apr-2025`)
              + ifelse(is.na(`May-2025`) == TRUE, 0, `May-2025`)
              + ifelse(is.na(`Jun-2025`) == TRUE, 0, `Jun-2025`),
         FY26 = ifelse(is.na(`Jul-2025`) == TRUE, 0, `Jul-2025`)
              + ifelse(is.na(`Aug-2025`) == TRUE, 0, `Aug-2025`)
              + ifelse(is.na(`Sep-2025`) == TRUE, 0, `Sep-2025`)
              + ifelse(is.na(`Oct-2025`) == TRUE, 0, `Oct-2025`)
              + ifelse(is.na(`Nov-2025`) == TRUE, 0, `Nov-2025`)
              + ifelse(is.na(`Dec-2025`) == TRUE, 0, `Dec-2025`)
              + ifelse(is.na(`Jan-2026`) == TRUE, 0, `Jan-2026`)
              + ifelse(is.na(`Feb-2026`) == TRUE, 0, `Feb-2026`)
              + ifelse(is.na(`Mar-2026`) == TRUE, 0, `Mar-2026`)
              + ifelse(is.na(`Apr-2026`) == TRUE, 0, `Apr-2026`)
              + ifelse(is.na(`May-2026`) == TRUE, 0, `May-2026`)
              + ifelse(is.na(`Jun-2026`) == TRUE, 0, `Jun-2026`)) |>
  select(Title, Vendor, Online_ISSN, Print_ISSN, ISBN, FY21, FY22, FY23, FY24, FY25, FY26, Reporting_Period_Total) |>
  mutate(`Classification Code` = 'Not Available')

colnames(TR_No_ID) <- c('Title', 'Vendor', 'Online_ISSN', 'Print_ISSN', 'ISBN', 'FY21', 'FY22', 'FY23', 'FY24', 'FY25', 'FY26', 'Reporting_Period_Total', 'Classification Code')
```





## Assign LC Codes for Subject-Specific Vendors

For the remaining Unknown LC items from Alma, and the usage with no identifiers at all, some may be able to be estimated based on its vendor. Vendors whose publishing areas are only in one LC letter can be generally assigned to that letter.

For example, IEEE (the Institute of Electrical and Electronics Engineers) is fully focused on the T LC codes, so we can generalize its usage to being a T vendor.



```{r}
joinedNotUnknown <- joined |>
  filter(`Classification Code` != 'Unknown') |>
  select(Title.x, Vendor, Online_ISSN, Print_ISSN, ISBN, FY21, FY22, FY23, FY24, FY25, FY26, Reporting_Period_Total, `Classification Code`) |>
  distinct()

colnames(joinedNotUnknown) <- c('Title', 'Vendor', 'Online_ISSN', 'Print_ISSN', 'ISBN', 'FY21', 'FY22', 'FY23', 'FY24', 'FY25', 'FY26', 'Reporting_Period_Total', 'Classification Code')
```


### Get the Vendors with Unknown LCs, No Joins, and No Identifiers

```{r}
joinedUnknown <- joined |>
  filter(`Classification Code` == 'Unknown') |>
  select(Title.x, Vendor, Online_ISSN, Print_ISSN, ISBN, FY21, FY22, FY23, FY24, FY25, FY26, Reporting_Period_Total, `Classification Code`)

colnames(joinedUnknown) <- c('Title', 'Vendor', 'Online_ISSN', 'Print_ISSN', 'ISBN', 'FY21', 'FY22', 'FY23', 'FY24', 'FY25', 'FY26', 'Reporting_Period_Total', 'Classification Code')


allMissingTitles <- rbind(TR_No_ID, usageJoinMisses, joinedUnknown)

allMissingTitles
```



## Assign LC Codes to the allMissingTitles

As new vendors appear or need to be edited, add or edit rows in the case_when() statement below.

```{r}
missingTitleLC <- allMissingTitles |>
  mutate(`Classification Code` = case_when(
    Vendor == 'IEEE' ~ 'T',
    Vendor == 'AMS' ~ 'Q',
    Vendor == 'AIAA' ~ 'Q',
    Vendor == 'AccessEngineering' ~ 'T',
    Vendor == 'CABIntl' ~ 'S',
    Vendor == 'RSC' ~ 'Q',
    Vendor == 'ASME' ~ 'T',
    Vendor == 'ASMIntl' ~ 'T',
    Vendor == 'SIAM' ~ 'Q',
    Vendor == 'ASCE' ~ 'T',
    Vendor == 'Karger' ~ 'R',
    Vendor == 'Thieme' ~ 'R',
    Vendor == 'AccessMedicine' ~ 'R',
    Vendor == 'DramaOnline' ~ 'N',
    Vendor == 'PsychOnline' ~ 'R',
    Vendor == 'ACS' ~ 'Q',
    Vendor == 'ACM' ~ 'T',
    Vendor == 'JPSJ' ~ 'Q',
    Vendor == 'AIPScitation' ~ 'Q',
    Vendor == 'Scientific' ~ 'T',
    Vendor == 'Rotunda' ~ 'E',
    Vendor == 'AmPhytoSoc' ~ 'Q',
    Vendor == 'MSP' ~ 'Q',
    Vendor == 'JAMA' ~ 'R',
    Vendor == 'JSTAGE' ~ 'R',
    Vendor == 'JBE' ~ 'P',
    Vendor == 'AAPediatrics' ~ 'R',
    Vendor == 'APHA' ~ 'R',
    Vendor == 'CSP' ~ 'Q',
    Vendor == 'OvidSP' ~ 'R',
    Vendor == 'CSIRO' ~ 'Q',
    Vendor == 'APA' ~ 'R',
    Vendor == 'AAAS' ~ 'Q',
    Vendor == 'APS' ~ 'Q',
    Vendor == 'AmerPhysicalSoc' ~ 'Q',
    Vendor == 'NEJM' ~ 'R',
    Vendor == 'Diabetes' ~ 'R',
    Vendor == 'GSP' ~ 'G',
    Vendor == 'PhilDocCenter' ~ 'B',
    Vendor == 'Slack' ~ 'R',
    .default = 'Unknown'
  ))

missingTitleLC
```


## Fill in Highly-Used Titles

Some highly used titles, especially newspapers, can be fit into an LC classification to further cut down on the Unknown tier. These can be added as much as desired for increased accuracy, but some level of inaccuracy will exist unless all titles are manually input (which is perfectly fine - make sure to say as such if using this code in reporting).


```{r}
missingTitleLC2 <- missingTitleLC |>
  mutate(`Classification Code` = case_when(
    Title == 'Oxford English Dictionary' ~ 'A',
    Title == 'A Course in Mathematical Modeling' ~ 'Q',
    Title == 'A Critical Introduction to the Study of Religion' ~ 'B',
    Title == 'Clinical Small Animal Internal Medicine' ~ 'R',
    Title == 'PLOS Pathogens' ~ 'R',
    Title == 'PLOS Computational Biology' ~ 'R',
    Title == 'PLOS Genetics' ~ 'R',
    Title == 'PLOS Biology' ~ 'R',
    Title == 'Government and Politics in Tennessee' ~ 'J',
    Title == 'Toxic Plants of North America, Second Edition' ~ 'S',
    Title == 'PLOS Medicine' ~ 'R',
    .default = `Classification Code`
  ))
```



```{r}
unknownTitles <- missingTitleLC2 |>
  filter(`Classification Code` == 'Unknown')

unknownTitles
```

## Check for Usage in the Unknown Tier

This is where you can check how much Unknown usage remains. A rate of under 10% of the total is usually solid enough for general reporting, unless told otherwise.

```{r}
test <- missingTitleLC2 |>
  group_by(`Classification Code`) |>
  summarise(Titles = n(),
            Usage = sum(Reporting_Period_Total))

sum(test$Usage)
```


# Get all Titles Back Together

```{r}
allTitles <- rbind(joinedNotUnknown, missingTitleLC2) |>
  distinct() |>
  mutate(TopClassification = ifelse(`Classification Code` == 'Unknown', 'Unknown', substr(`Classification Code`, 1, 1)))

allTitles
```


## Save the Usage with LC to Excel and the Database


```{r, warning = FALSE}
setwd('C:\\Users\\aharrima\\OneDrive - University of Tennessee\\Documents\\One-Off Usage Analysis\\Adding LC Codes to Usage') #Set this also to where you want the data to be saved on your computer!

write_xlsx(allTitles, 'LC Codes for All Electronic Usage Archive with FY Usage.xlsx')

dbWriteTable(con, 'TR_Archive_Usage_by_LC', allTitles, overwrite = TRUE)
```


Using the new TR_Archive_Usage_by_LC table, update the PowerBI's Usage by LC Code page. If you need only one-shot information, continue below.


# Get Confirmed Usage by LC Code


```{r}
lcUsage <- allTitles |>
  group_by(`Classification Code`) |>
  summarise(Titles_Found = length(unique(Title)),
            FY21 = round(sum(FY21), 0),
            FY22 = round(sum(FY22), 0),
            FY23 = round(sum(FY23), 0),
            FY24 = round(sum(FY24), 0),
            FY25 = round(sum(FY25), 0),
            FY26 = round(sum(FY26), 0),
            Reporting_Period_Total = round(sum(Reporting_Period_Total), 0)) |>
  arrange(`Classification Code`)

lcUsage
```


# Get Confirmed Usage by LC Letter


```{r}
lcLetterUsage <- allTitles |>
  mutate(`Classification Letter` = ifelse(`Classification Code` != 'Unknown', substr(`Classification Code`, 1, 1), 'Unknown')) |>
  group_by(`Classification Letter`) |>
  summarise(Titles_Found = length(unique(Title)),
            FY21 = round(sum(FY21), 0),
            FY22 = round(sum(FY22), 0),
            FY23 = round(sum(FY23), 0),
            FY24 = round(sum(FY24), 0),
            FY25 = round(sum(FY25), 0),
            FY26 = round(sum(FY26), 0),
            Last_5_Years_Usage = round(sum(Reporting_Period_Total), 0)) |>
  arrange(`Classification Letter`) |>
  mutate(Last_5_Years_Usage = ifelse(`Classification Letter` == 'Unknown', Last_5_Years_Usage + 38, Last_5_Years_Usage),
         FY21 = ifelse(`Classification Letter` == 'Unknown', FY21 + 4, FY21),
         FY22 = ifelse(`Classification Letter` == 'Unknown', FY22 + 8, FY22),
         FY23 = ifelse(`Classification Letter` == 'Unknown', FY23 + 8, FY23),
         FY24 = ifelse(`Classification Letter` == 'Unknown', FY24 + 8, FY24),
         FY25 = ifelse(`Classification Letter` == 'Unknown', FY25 + 8, FY25),
         FY26 = ifelse(`Classification Letter` == 'Unknown', FY26 + 4, FY26))


lcLetterUsage
```


# Save the Usage by LC Code

If you need to only share an Excel file with this information, use this to save it.

```{r, warning = FALSE}
setwd('C:\\Users\\aharrima\\OneDrive - University of Tennessee\\Documents\\One-Off Usage Analysis\\Adding LC Codes to Usage') #The data will be saved to this folder again!

write_xlsx(lcLetterUsage, 'Last Five Years Unique Item Requests by LC Code and Fiscal Year.xlsx')
```




